Analysis paper

### 2021-06-03 analysis/analysis.Rmd
add ensemble member plot

>>>>

#### Number of members in the ensemble
```{r}
ens <- ensemble_members[, .("GM_inc_case" = sum(GM_inc_case), 
                     "PL_inc_case" = sum(PL_inc_case), 
                     "GM_inc_death" = sum(GM_inc_death), 
                     "PL_inc_death" = sum(PL_inc_death)), 
                 by = "Date"] %>%
  melt(id.vars = "Date")

ens[, .(mean = mean(value), 
       median = median(value)), by = "variable"]

p <- ens %>%
  ggplot(aes(y = value, x = Date, color = variable)) + 
  geom_line()

ggsave(here("analysis", "plots", "ensemble-members.png"), 
       plot = p)
